---
output:
    github_document
R-Package: mpcadb
Version: 0.0.0.9000
---

# mpcadb

:electric_plug: :floppy_disk: Easy R connections to MPCA's databases: DELTA, TEMPO, EQUIS, RAPIDS, ONBASE.


## Functions

* `open_delta` : Open a connection to _DELTAW_, MPCA's oracle database that houses TEMPO, EQUIS, RAPIDS, ONBASE and more.
* `get_ai` : Get all Agency Interest (AI) names from TEMPO.

```{r, include=F}
library(knitr)
```

## Install

Install `mpcadb` from GitHub:

```{r, eval=F}
# First install the 'devtools' package
library(devtools)

# Install the development pkg from GitHub
remotes::install_github("MPCA-data/mpcadb")
```
-----


## Use

Open an RODBC connection to DELTA with the `open_delta()` function. It will add the credentials for you.

```{r}
library(mpcadb)

# Open DELTA connection and set to `deltaw`
deltaw <- open_delta()

```

<br>


## TEMPO AI's

Get a complete list of the Agency Interests from TEMPO with `get_ai()`:

```{r}
ai_names <- get_ai(keep_alt_names = TRUE)

kable(head(ai_names, 4))
```


<br>


Get only a select list of TEMPO AI's:
```{r}
ai_names <- get_ai(ai = c(441, 288), keep_alt_names = FALSE)

kable(ai_names)
```


<br>

## EQUIS examples...

<br>
